Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
some revision of sec 4.5

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with precision and sampling rate incrementation}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

 \end{tikzpicture}
}}
\caption{The CEGIS loop with precision and sampling rate incrementation}
\label{fig:CEGIS-precision-increment}
\end{figure}

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$. It does this by assuming 
a $k$ and a sampling rate. The check that this assumptions were sound 
is performed later by the {\sc complete} and {\sc sampling} 
validation stages.

2. The validation phase consists of four stages 
(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
performs potentially unsound operations assuming a plant's precision $<I_p,F_p>$, 
current $k$ and sampling rate, whereas the subsequent three stages are used to 
restore soundness.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with incremental precision, completeness threshold and sampling rate}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

 \end{tikzpicture}
}}
\caption{The CEGIS loop with incremental precision, 
completeness threshold and sampling rate.}
\label{fig:CEGIS-precision-increment}
\end{figure}

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$. It does this by assuming 
a plan't precision $<I_p,F_p>$, a $k$ and a sampling rate. 
The check that these assumptions are sound 
is performed later by the {\sc complete} and {\sc sampling} 
validation stages.

2. The validation phase consists of four stages 
(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
performs potentially unsound operations considering the currently assumed 
plant's precision $<I_p,F_p>$, 
$k$ and sampling rate, whereas the subsequent three stages are used to 
restore soundness.
